Towards Transparency and Open Science

### 2023-01-22 manuscript.Rmd
decrease fontsize

  \usepackage{polyglossia}
  \setmainlanguage[]{english}
  \setotherlanguage[]{german}
fontsize: 12pt
linestretch: 1.2
geometry: "left=3.6cm, right=3.6cm, top=4cm, bottom=4cm, bindingoffset=5mm"
classoption: twoside
papersize: a4
bibliography: references.bib
abstract: "`r paste0(c('\\\\setstretch{1.0}English:', readLines('abstract.md'), '\\\\par Deutsch:\\\\textgerman{', readLines('zusammenfassung.md'), '}\\\\newpage'), collapse = ' ')`"
csl: apa.csl
toc: false # it is manually placed
repro:
  files:
    - abstract.md
    - apa.csl
    - papers/
  tlmgr:
    - pgf
    - preview
    - libertine
    - pdfpages
  apt:
    - git
    - rsync
---

>>>>

  \usepackage{polyglossia}
  \setmainlanguage[]{english}
  \setotherlanguage[]{german}
fontsize: 11.5pt
linestretch: 1.2
# https://practicaltypography.com/page-margins.html
# 3.81 to 5.08cm or 45-90 characters or 2-3 alphabets
geometry: "left=4cm, right=4cm, top=3.5cm, bottom=4.5cm, bindingoffset=5mm"
classoption: twoside
papersize: a4
bibliography: references.bib
abstract: "`r paste0(c('\\\\setstretch{1.0}English:', readLines('abstract.md'), '\\\\par Deutsch:\\\\textgerman{', readLines('zusammenfassung.md'), '}\\\\newpage'), collapse = ' ')`"
csl: apa.csl
toc: false # it is manually placed
repro:
  files:
    - abstract.md
    - apa.csl
    - papers/
  tlmgr:
    - pgf
    - preview
    - libertine
    - pdfpages
  apt:
    - git
    - rsync
---
